New insights into the Weddell Sea ecosystem applying a network approach

### 2022-12-13 Manuscript/Manuscript.Rmd
Added Intro (v. 13/12)

<!-- about food webs and interaction strength -->
Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012]. Although analyses considering presence/absence data on predator-prey interactions have provided insights about the structure and functioning of communities [e.g. @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability. In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015].

<!-- General description of the Weddell Sea -->
The Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica and is still largely unprotected [@Teschke2021]. This region is less affected by sea surface warming compared with other areas like the Antarctic Peninsula, which is more exposed. If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted benthonic species [@Griffiths2017].

> * Food webs studies about Weddell Sea
> * Key species or species role

The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes. To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.

>>>>

<!-- Intro & advantages of studying food webs -->
Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012]. Although analyses considering presence/absence data on predator-prey interactions have provided insights about the structure and functioning of communities [e.g. @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability. In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015; @Nilsson2016].

<!-- Interaction strength -->
Several methodologies have been applyied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determines which approach is more convenient [@Berlow2004].

<!-- General description of the Weddell Sea -->
The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean. About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E. The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021]. It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020]. Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea. These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].

<!-- Food webs studies about Weddell Sea / Key species or species role -->

<!-- Importance of these studies for climate change & conservation -->
The Weddell Sea region is less affected by sea surface warming compared with other areas of the Southern Ocean. If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted benthonic species [@Griffiths2017].

<!-- Objective -->
The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes. To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
